### 2015-04-07 cug_paper/05_conclusion.tex
Scott's conclusion edits

The results for the second test series (16 ranks/node) are less clear.  As with the first test series, write sizes need to be at least 4MB Looking closely at Figure \ref{fig:results_base_16} and Figure \ref{fig:results_16_nobars}, it appears that write sizes that can fit into GPU memory perform slightly better than just writing to disk.  However, write sizes that exceed the capacity of the GPU's memory are actually a little slower than writing straight to the filesystem.

There are several other complications to consider, though.
First, Since the test application did no actual computation, there were plenty of cores available for the daemon to execute on.  In a real HPC application, this wouldn't be the case and the application's performance would almost certainly be negatively affected by the context switches.  On the other hand, an application that is running 16 ranks/node is unlikely to leave much system memory free for use by the Lustre client-side cache.  So, the improvement from caching writes in GPU memory might offset the disruption caused by oversubscribing the cores.  Whether or not this technique provides a net performance improvement in such a configuration will probably depend on the particular application.

An interesting compromise might be to have the application run 15 ranks/node instead of 16.  That will leave 1 core available for the daemon.  Both threads could be pinned to that core, with the message processing thread given higher priority.  It would also be possible to use the  core specialization option to aprun to schedule OS tasks on that core.  Compared to an application running lots of MPI collectives, the daemon isn't particularly sensitive to short interrupts like that.  This configuration hasn't been tested and the authors are unaware of any application that routinely runs with 15 ranks/node.

In general, the results show that using the GPU memory to cache filesystem writes provides approximately the same performance as the Lustre client-side cache.  The difference is that the Lustre cache uses system memory which may not actually be available.  Even if it is, the user must ensure that writes are spread across a sufficient number of OST's to make sue of it.  Neither of these conditions apply when using GPU memory as a cache.

>>>>

The results for the second test series (16 ranks/node) are less clear.  As with the first test series, write sizes need to be at least 4MB Looking closely at Figure \ref{fig:results_base_16} and Figure \ref{fig:results_16_nobars}, it appears that write sizes that can fit into GPU memory perform slightly better than just writing to disk.  However, write sizes that exceed the capacity of the GPUs memory are actually a little slower than writing straight to the filesystem.

There are several other complications to consider, though.
First, Since the test application did no actual computation, there were plenty of cores available for the daemon to execute on.  In a real HPC application, this would not be the case and the application's performance would almost certainly be negatively affected by the context switches.  On the other hand, an application that is running 16 ranks/node is unlikely to leave much system memory free for use by the Lustre client-side cache.  So, the improvement from caching writes in GPU memory might offset the disruption caused by oversubscribing the cores.  Whether or not this technique provides a net performance improvement in such a configuration will probably depend on the particular application.

An interesting compromise might be to have the application run 15 ranks/node instead of 16.  That will leave 1 core available for the daemon.  Both threads could be pinned to that core, with the message processing thread given higher priority.  It would also be possible to use the  core specialization option to aprun to schedule OS tasks on that core.  Compared to an application running lots of MPI collectives, the daemon is not particularly sensitive to short interrupts like that.  This configuration has not been tested and the authors are unaware of any application that routinely runs with 15 ranks/node.

In general, the results show that using the GPU memory to cache filesystem writes provides approximately the same performance as the Lustre client-side cache.  The difference is that the Lustre cache uses system memory which may not actually be available.  Even if it is, the user must ensure that writes are spread across a sufficient number of OSTs to make use of it.  Neither of these conditions apply when using GPU memory as a cache.
